The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2022-03-04 src/paper/report.tex
Add reference for susceptibility by age to main text.

In the model, susceptibility to contracting the SARS-CoV-2 virus is dependent on age. A
possible infection progresses as shown in Figure~\ref{fig:model_disease_progression}. We
differentiate between an initial period of infection without being infectious or showing
symptoms, being infectious (presymptomatic or asymptomatic), showing symptoms, requiring
intensive care, and recovery or death \citep[similar to][]{Aleta2020}. The probabilities
of transitioning between these states depend on age; their duration is random and
calibrated to medical literature (for a detailed description see Supplementary
Material~\ref{sub:data_course_of_disease}). Conditional on the type of contact,
infectiousness is independent of age \citep{Jones2021}.

>>>>

In the model, susceptibility to contracting the SARS-CoV-2 virus is dependent on
age \citep{Davies2020}. A possible infection progresses as shown in
Figure~\ref{fig:model_disease_progression}. We differentiate between an initial
period of infection without being infectious or showing symptoms, being
infectious (presymptomatic or asymptomatic), showing symptoms, requiring
intensive care, and recovery or death \citep[similar to][]{Aleta2020}. The
probabilities of transitioning between these states depend on age; their
duration is random and calibrated to medical literature (for a detailed
description see Supplementary Material~\ref{sub:data_course_of_disease}).
Conditional on the type of contact, infectiousness is independent of age
\citep{Jones2021}.
